---
title: "JGipson Live Session Unit  3 Assignment"
author: "Johnny Gipson"
date: "September 15, 2018"
output: html_document
---
#Questions 1: Github Cloning
Git Bash was used and the following code was to create and new directory, navigate, and clone the gut hub Repository

Git bash code:

pwd

mkdir JohnnyGipson

cd JohnnyGipson

git clone https://github.com/caesar0301/awesome-public-datasets

#Question 2a: Read Titantic Data Set and Create Data Frame

```{r, echo=TRUE}
Ship <-read.csv(file='C:/Users/Johnny Gipson/Desktop/titanic.csv', header=TRUE)
class (Ship)
dim (Ship)
names (Ship)
```

#Question 2b:  Frequency Plot of Male and Female

```{r, echo=TRUE}
library ("ggplot2")
Shipfreq <-ggplot (Ship) + geom_bar(aes(x=Sex, fill = Sex))
Shipfreq + ggtitle ("Frequency of Males and Females on the Titanic")
```

#Question 2c: Use one of apply functions to get the means of Age, Fare, Survival

```{r, echo=TRUE}
lapply (Ship["Age"], mean, na.rm=TRUE)
lapply (Ship["Fare"], mean, na.rm=TRUE)
lapply (Ship["Survived"], mean, na.rm=TRUE)
```

#Question 3a - Create Objects for median age, Min and Max Duration of Sleep, Mean and Standard Deviation of RSESS

```{r, echo=TRUE}
sleep <-read.csv(file='C:/Users/Johnny Gipson/Desktop/sleep_data_01.csv', header=TRUE)
class(sleep)
dim (sleep)
names (sleep)
MedAge <-function(x) { median(x,na.rm=TRUE)}
MedAge(sleep$Age)
MinDuration <-function (x) {min(x,na.rm=TRUE)}
MinDuration (sleep$Duration)
MaxDuration <-function (x) {max(x,na.rm=TRUE)}
MaxDuration (sleep$Duration)
MEANRSES <-function(x) {mean(x,na.rm=TRUE)}
MEANRSES(sleep$RSES)
SDRSES <-function(x) {sd(x,na.rm=TRUE)}
SDRSES(sleep$RSES)
```

##Question 3b - Create Data Frame with New Objects
```{r, echo=TRUE}
sleepa<-function (x) {data.frame("medianage"= MedAge(sleep$Age),"RSESMean"= MEANRSES(sleep$RSES)/5,"SDRSES"=SDRSES(sleep$RSES)/5, "RangeofDuration"= (MaxDuration(sleep$Duration)-MinDuration(sleep$Duration)))}
report<-sleepa(sleep)
report
```

##Question 3c - Change column names of dataframe 
```{r, echo=TRUE}
library(data.table)
chgname <- function(x) {setnames(x, old=c("medianage","RSESMean","SDRSES","RangeofDuration"), new=c("MedianAge","SelfEsteem","SE_SD","DurationRange"))}
chgname(report)
report
```

##Question 3d - Round the Report to 2 digits
```{r, echo=TRUE}
rreport <-function(x) {round(x,2)}
rreport(report)
```

##Questions 3e: Run function on your sleep Data
```{r, echo=TRUE}
sleep <-read.csv(file='C:/Users/Johnny Gipson/Desktop/sleep_data_01.csv', header=TRUE)
class(sleep)
dim (sleep)
names (sleep)
MedAge <-function(x) { median(x,na.rm=TRUE)}
MedAge(sleep$Age)
MinDuration <-function (x) {min(x,na.rm=TRUE)}
MinDuration (sleep$Duration)
MaxDuration <-function (x) {max(x,na.rm=TRUE)}
MaxDuration (sleep$Duration)
MEANRSES <-function(x) {mean(x,na.rm=TRUE)}
MEANRSES(sleep$RSES)
SDRSES <-function(x) {sd(x,na.rm=TRUE)}
SDRSES(sleep$RSES)
sleepa<-function (x) {data.frame("medianage"= MedAge(sleep$Age),"RSESMean"= MEANRSES(sleep$RSES)/5,"SDRSES"=SDRSES(sleep$RSES)/5, "RangeofDuration"= (MaxDuration(sleep$Duration)-MinDuration(sleep$Duration)))}
report<-sleepa(sleep)
report
library(data.table)
chgname <- function(x) {setnames(x, old=c("medianage","RSESMean","SDRSES","RangeofDuration"), new=c("MedianAge","SelfEsteem","SE_SD","DurationRange"))}
chgname(report)
report
rreport <-function(x) {round(x,2)}
rreport(report)
```

##Question 4a:  Install the fivethirtyeight package

Code for install - install.packages("fivethirtyeight")
```{r, echo=TRUE}
library("fivethirtyeight")
```

##Question 4b:Assign the 22nd data set to an object 'df'
```{r, echo=TRUE}
data(package="fivethirtyeight")
class(college_recent_grads)
df<-data.frame(college_recent_grads)
```

##Question 4C - URL to the related story
The first r code used to find the URL came back with a warning message that it could not be found.  So a detail seach on the entire list was made to the URL.
The URL to the college recent data is http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/

```{r, echo=TRUE}
vignette("college_recent_grads", package = "fivethirtyeight")
vignette("fivethirtyeight", package = "fivethirtyeight")
```

##Question 4D - Get the dimensions and column names of df
```{r, echo=TRUE}
dim(df)
colnames(df)
```

##Question 5a -Give column names and count the columns
```{r, echo=TRUE}
colnames(df)
ncol(df)
```

##Question 5b - Generate a count of each unique Major_category in a data frame
```{r, echo=TRUE}
library (plyr)
x<-count(df$major_category)
major_count<-as.data.frame(x, row.names=NULL)
class (major_count)
major_count
```

##Question 5c- Create barplot of frequency - to much great coding in ggplot to go to waste. Using barplot() is question 5c.1
```{r, echo=TRUE}
library(gcookbook)
MC<-ggplot(major_count, aes(x=x,y=freq)) + geom_bar(stat="identity", fill="blue", colour="black")+coord_flip()
MC + ggtitle ("College Majors Picked by Today's College Student") + xlab("College Majors") +ylab ("Frequency")
```

##Question 5c.1- Create barplot of frequency using barplot()
```{r, echo=TRUE}
par(las=2,barplot(major_count$freq, names.arg=major_count$x, horiz=TRUE,col="purple",main="College Majors Picked by Today's College Student", xlab="College Majors", ylab="Frequency" ))
```

##Question 5d -Write fivethirtyeight data to csv file
```{r, echo=TRUE}
write.csv(df,"C:/Users/Johnny Gipson/Desktop/college_recent_grads.csv",row.names=FALSE)

```

##Question 6 Link to my github repository
https://github.com/jlgipson/MSDS6306


