---
title: "JGipson_Assignment5"
author: "Johnny Gipson"
date: "September 24, 2018"
output: html_document
---

##Install libraries
```{r, echo =TRUE}
library(tidyr)
library(plyr)
library(dplyr)
library(bitops)
library(RCurl)
library(xml2)
library(rvest)
library(XML)
library(ggplot2)
library(gcookbook)
```

##Question 1a: Import data file and assign it as data frame object, df
```{r, echo =TRUE}
df<-read.table(file='C:/Users/Johnny Gipson/Desktop/yob2016.txt', sep=";", col.names=c("First_Name", "Gender", "Amount_of_Children"))
str(df)
```

##Question 1b: Display the summary and Structure of df
```{r, echo =TRUE}
summary (df)
dim(df)
str(df)
head (df)
```

##Question 1c:  FInd the name with the 'yyy'
```{r, echo =TRUE}
grep("yyy",df$First_Name)
df[212,]
```

##Question 1d: Remove misspelled word from the dataframe 
```{r, echo =TRUE}
y2016<-df[-212,]
grep("yyy",y2016$First_Name)
str(y2016)
head(y2016)
```

##Question 2a: Import data file and assign it as data frame object, df
```{r, echo =TRUE}
y2015<-read.table(file='C:/Users/Johnny Gipson/Desktop/yob2015.txt', sep=",", col.names=c("First_Name", "Gender", "Amount_of_Children"))
str(y2015)
```

##Question 2b: Look at the last ten rows
```{r, echo =TRUE}
tail(y2015, 10)
```
Comment: It is surprising that the baby names that begin with Z have the same amount of children.

##Question 2c: Merge y2016 and y2015
```{r, echo =TRUE}
dim(y2015)
dim(y2016)
final<-merge(y2016,y2015,by="First_Name", type="inner", match="all")
dim(y2016)
dim(final)
str(final)
head(final)
```

##Question 3a -Create Total Column
```{r, echo =TRUE}
final<-mutate(final, Total = Amount_of_Children.x+Amount_of_Children.y)
head(final)
```

##Question 3b - Sort the data by Total
```{r, echo =TRUE}
final_sort<-final[order(final$Total, decreasing=TRUE),]
head(final_sort,20)
```

##Question 3c -Top 10 Girl Names
```{r, echo =TRUE}
final_girl<-subset(final_sort, final_sort$Gender.x=="F"& final_sort$Gender.y=="F")
head(final_girl, 10)
Top_Ten_Girl_Names<-final_girl[1:10,]
Top_Ten_Girl_Names
```

##Question 3d - Write cvs of Top Ten Girl Names
```{r, echo =TRUE}
Top_Ten_Girl_Names<-Top_Ten_Girl_Names[,-(2:5)]
Top_Ten_Girl_Names
write.csv(Top_Ten_Girl_Names, file = 'C:/Users/Johnny Gipson/Desktop/Top_Ten_Girl_Names.cvs',row.names=FALSE)
```

##Question 4:  Upload to HW to Github
https://github.com/jlgipson/MSDS6306/tree/master/HOMEWORK