---
title: "CaseStudy_Codebook"
author: "Johnny Gipson"
date: "October 8, 2018"
output: html_document
---

##Summary

##Files & Desrciption
Beers. csv - A list of 2410 US craft beers
Breweries.csv - A list of 558 breweries

Both files are located are located at https://github.com/jlgipson/MSDS6306/tree/master/CaseStudy

##Variables
Beers.csv:
Name: Name of the beer.
Beer_ID: Unique identifier of the beer.
ABV: Alcohol by volume of the beer.
IBU: International Bitterness Units of the beer.
Brewery_ID: Brewery id associated with the beer.
Style: Style of the beer.
Ounces: Ounces of beer.

Breweries.csv:
Brew_ID: Unique identifier of the brewery.
Name: Name of the brewery.
City: City where the brewery is located.
State: U.S. State where the brewery is located.



##Libraries needed for Analysis
```{r, echo=TRUE}
library(tidyr)
library(plyr)
library(dplyr)
library(bitops)
library(RCurl)
library(xml2)
library(rvest)
library(XML)
library(ggplot2)
library(gcookbook)
```
##Question 1: How many brewies are present in each state
```{r, echo=TRUE, fig.width=14}
Breweries<-read.csv(file='C:/Users/Johnny Gipson/Desktop/Breweries.csv')
dim(Breweries)
str(Breweries)
head(Breweries, 10)
tail(Breweries,10)
Breweries_state<-summarise(group_by(Breweries,State), count=n())
Breweries_state
Breweries_state<-data.frame(Breweries_state)
dim(Breweries_state)
str(Breweries_state)
head(Breweries_state,10)
Breweries_graph<-ggplot(Breweries_state, aes(x=State,y=count, fill=State)) + geom_bar(stat="identity", colour="black", position=position_dodge(0.7))
Breweries_graph + ggtitle ("Number of Breweries  per State ") + xlab("States") +ylab ("Number of Breweries") + theme(axis.text.x = element_text(vjust=0.3,hjust=0.3, angle=90))+theme(plot.title=element_text(hjust=0.5,size=16,face="bold.italic"))
```

##Question 2: Merge beer data with Breweries Data
```{r, echo=TRUE,}
Beers<-read.csv(file='C:/Users/Johnny Gipson/Desktop/Beers.csv')
dim(Beers)
str(Beers)
head(Beers, 10)
tail(Beers,10)
Brew_beer<-merge(Breweries,Beers, by.x=c("Brew_ID"),by.y=c("Brewery_id"))
dim(Brew_beer)
str(Brew_beer)
head(Brew_beer, 10)
tail(Brew_beer, 10)
```

##Question 3: Count the number of NAs in each column
```{r, echo=TRUE,}
sum(is.na(Brew_beer))
sapply(Brew_beer,function(x)sum(is.na(x)))
```

##Question 4:Compute the median ABV and IBU for each state and plot
```{r, echo=TRUE,fig.width=14}
median_woNAs <- function(x) {median(x[which(!is.na(x))])}
State_ABV<-tapply(Brew_beer$ABV, Brew_beer$State,median_woNAs)
State_IBU<-tapply(Brew_beer$IBU, Brew_beer$State,median_woNAs)
State_ABV<-aggregate(Brew_beer$ABV, list(Brew_beer$State),median_woNAs)
State_IBU<-aggregate(Brew_beer$IBU, list(Brew_beer$State),median_woNAs)
colnames(State_ABV) <-c("State","ABV_Median")
colnames(State_IBU) <-c("State","IBU_Median")
State_beer<-merge(State_ABV,State_IBU, by= "State")
dim(State_beer)
str(State_beer)
head(State_beer)
tail(State_beer)
States_graphabv<-ggplot(State_beer, aes(x=State,y=ABV_Median, fill=State)) + geom_bar(stat="identity", colour="black", position=position_dodge(0.7))
States_graphabv + ggtitle ("ABV_Median by State") + xlab("States") +ylab ("ABV_Median") + theme(axis.text.x = element_text(vjust=0.3,hjust=0.3, angle=90))+theme(plot.title=element_text(hjust=0.5,size=16,face="bold.italic"))
States_graphibu<-ggplot(State_beer, aes(x=State,y=IBU_Median, fill=State)) + geom_bar(stat="identity", colour="black", position=position_dodge(0.7))
States_graphibu + ggtitle ("IBU_Median by State") + xlab("States") +ylab ("IBU_Median") + theme(axis.text.x = element_text(vjust=0.3,hjust=0.3, angle=90))+theme(plot.title=element_text(hjust=0.5,size=16,face="bold.italic"))
```
Check Data Set, SD breweries have no IBUs in the data set

##Question 5: Which State has the maximum ABV and which stat has the highest IBU.

Kentucky has the highest ABV.  Maine has the highest IBU

##Question 6:Summary statistics for the ABV Variable
The first is summary statistic of the ABV median variable that was creaed in Question 4.  The second summary statistic is of the merge data of brewery and beer data set in Question 2.
```{r, echo=TRUE}
summary(State_beer$ABV_Median)
summary(Brew_beer$ABV)
```

##Question 7:
```{r, echo=TRUE}
str(Brew_beer)
ggplot(Brew_beer, aes(x=ABV, y=IBU)) +geom_point()
```
There appears to be a positive relationship betwwwn ABV and IBU.  As the beer's ABV increases so does its IBU.  There are many outliers that do not follow this relationship showing high ABV and low to medium IBV.